---
output:
  github_document:
    html_preview: false
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

## Overview
`"binomial"` is a niminal [R](http://www.r-project.org/) pacjage that provides functions to obtain statistics for binomial distributions.

* `bin_choose()` calculates the number of combinations possible for `k` successes in `n` trials.
* `bin_probability()` calculates the probability of getting `k` successes in `n` trials.
* `bin_distribution()` returns a data frame of class `bindis`. The number of successes is in the first column, and the probability of the corresponding number of successes is in the second.
* `plot()` is a method for bin_distribution that takes an input of class `bindis`, creating a barplot for the successes and their probabilities.
* `bin_cumulative()` returns a data frame of the class `bincum`. The number of succeses is in the first column, the probability of the corresponding success is in the second, and the cumulative probabilities are in the third.
* `plot()` is a method also used for an input of class `bincum`. This creates a line graph.
* `bin_variable()` creates a named list of class `binvar` for trials and probabilities.
* `print()` method is used for `binvar` objects to print out the number of trials and probability.
* `summary()` method is used for `binvar` objects to compute summary statistics.
* `print.summary()` method is used for `summary.binvar` objects to print out the trials, probability, and the summary statistics.

## Motivation
The reason behind creating this package was to explore and learn how to create an R package using devtools. We have written RScripts for private and main functions and tests.

## Installation
To install the package from Github, use the package "devtools"
```{r}
# development version from Github:
#install.packages("devtools")

# install "binomial" (without vignettes)
#devtools::install_github("stat133-sp19/hw-stat133-jesskimy/tree/master/binomial")

# install "binomial" (with vignettes)
#devtools::install_github("stat133-sp19/hw-stat133-jesskimy/tree/master/binomial", build_vignettes = TRUE)
```

## Usage
```{r}
library(binomial)

#Combinations of 3 heads in 5 coin tosses
bin_choose(n = 5, k = 3)

#Probability of getting 3 heads in 5 coin tosses
bin_probability(3, 5, 0.5)

#Distribution of probabilities for 5 coin tosses
bin_distribution(5, 0.5)

#Plot the distribution
bindis2 <- bin_distribution(5, 0.5)
plot(bindis2)

#Cumulative probability distribution of 5 coin tosses
bin_cumulative(5, 0.5)

#Create a binomial random variable
bin_variable(5, 0.5)

#Summary of the binomial random variable
bin_summary <- bin_variable(5, 0.5)
summary(bin_summary)
```

