---
title: "Introduction to Binomial"
author: "Jessica Kim"
date: "`r Sys.Date()"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, echo = FALSE, message = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(binomial)
library(ggplot2)
```

## Binomial

The package "binomial" is an implementation for computing different statistics for binomial distributions. This includes the probabilities of success, expected value, variance, mode, skewness, and kurtosis of a binomial distribution. 

## Important Things to Note
There are some things to keep in mind about the inputs for the functions we are about to explore. 
For probability, or `prob` to be valid, it has to be a numeric value between 0 and 1, inclusive.
For `trials` to be valid, it must be a non-negative integer.
For `success` to be valid, it must be an integer or a vector of integers greater than or equal to 0 and less than or equal to the number of trials.
If any of the values are invalid, an error message will show up.

## Binomial Functions

## bin_choose()
We can find the number of combinations for which k successes can happen in n trials. 
The code below explains the number of combinations possible for 3 (heads) successes in 10 trials (coin tosses).
```{r}
bin_choose(10, 3)
```

## bin_probability()
The function `bin_probability()` gives us the probability of getting k successes in n trials, given a probability of success (in one trial). The code below would compute the probability of getting 3 (heads) successes in 10 trials (fair coin tosses).
```{r}
bin_probability(3, 10, 0.5)
```

## bin_distribution()
Next, the `bin_distribution()` function can be used to get the entire distribution. This function returns a data frame with the number of successes in the first column and the probability of the corresponding number of successes in the second column.
For example, the code below would display the distribution for 0 to 10 (heads) successes in 10 trials (fair coin tosses). 
```{r}
bin_distribution(trials = 10, prob = 0.5)
```
We can also plot this distribution by calling the method `plot()` after assigning the output of `bin_distribution()` to a variable, as shown below:
```{r, fig.show='hold'}
bindis1 <- bin_distribution(10, 0.5)
plot(bindis1)
```

## bin_cumulative()
Building off of the `bin_distribution()` function, `bin_cumulative()` returns the same data frame as from above, but with a third column that has the corresponding cumulative probabilities.
```{r}
bin_cumulative(trials = 10, prob = 0.5)
```
This can also be plotted with a method `plot()`, using the same format as above.
```{r, fig.show='hold'}
bincum1 <- bin_cumulative(10, 0.5)
plot(bincum1)
```

## bin_variable()
This function creates a binomial random variable. 
```{r}
bin_variable(trials = 10, prob = 0.5)
```
There is a summary function that we can use to access summary statistics of the binomial variable. It gives us the mean, variance, mode, skewness, and kurtosis.
```{r}
bin_var <- bin_variable(10, 0.5)
summary(bin_var)
```

## Summary Functions
Finally, we can use individual summary functions to only get the specific descriptive statistics.
```{r}
#mean
bin_mean(trials = 10, prob = 0.5)

#variance
bin_variance(trials = 10, prob = 0.5)

#mode
bin_mode(trials = 10, prob = 0.5)

#skewness
bin_skewness(trials = 10, prob = 0.5)

#kurtosis
bin_kurtosis(trials = 10, prob = 0.5)
```

